\section{Introduction}
\subsection{Topic}
IoT devices are on the rise and it is hard to imagine our everyday life without them. They make many everyday tasks easier, collect information or connect us with other people. New applications for these small and often practical devices are being added every day.
\newline
\newline
However, the majority of these IoT devices have a very large weak point. The data exchange of the IoT devices is often handled by the manufacturer of the devices. This means that if a manufacturer goes bankrupt, the IoT devices from this manufacturer often become useless, as the data exchange between the devices can no longer take place.
\newline
\newline
My goal is to start with exactly this rough problem. 
In this work we want to work out a way to break the dependency of the IoT devices to the manufacturers. It should be possible for us to operate our IoT devices without the communication via the manufacturer, and thus free us from the risk of a complete failure of our IoT infrastructure in the event of bankruptcy of the manufacturer. We will thus outsource the communication of the IoT devices to a broker. This broker will replace the manufacturer as a communication node and it should be possible for us to operate this broker locally (in the same network).
\newline
\newline
In this paper I will show you a more detailed insight into our new communication line, and I will also provide you with the most important information about the selected broker. 

\newpage
\subsection{What is a Broker}
The broker is a server or service that caches data from clients and makes it fetchable. It is our hub of communication between the IoT device that reads the sensors and the end device that analyzes the data or provides it to the client.
Data exchanged through a broker is often public and available for all to see. The challenge of storing data anonymously and making it unrecognizable to the extent that it cannot be read by third parties is mandatory for a broker when it comes to sensitive data.

\subsection{Freenet}


\subsection{Hardware}